Stimuli Selection

### 2024-10-03 study2/experiment/stimuli_selection/selection.qmd
Revert "stimuli 2"
This reverts commit a7dac3b662598a95344793d4146ca44d1df9cd63.

selection_erotic2 <- napsero2 |> 
  filter(ID %in% selected_erotic_2)

write.csv(selection_erotic2, "stimuli_data2.csv", row.names=FALSE)
knitr::kable(selection_erotic2)
```

```{r}
#| code-fold: true
json <- selection2 |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()

write(paste("var stimuli_list2 = ", json), "stimuli_list2.js")
```

>>>>

selection <- napsero |> 
  filter(ID %in% selected_erotic)

write.csv(selection, "stimuli_data.csv", row.names=FALSE)
knitr::kable(selection)
```

```{r}
#| code-fold: true
json <- selection |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()

write(paste("var stimuli_list = ", json), "stimuli_list.js")
```
